Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
FWL for f_b
fixed sec 4.3

$$
\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
$$

@@

This time the {\sc uncertainty} check doesn't find any more counterexamples 
and we pass the current candidate solution to the {\sc precision} verification stage.
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
We obtain the result $false$, meaning that the current precision is insuficient.
Consequently, we increase our precision to $I_b=20,F_b=28$.
%
Since the previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. Back in the {\sc synthesise}
phase, we re-start the process with a candidate solution with all coefficients 0.
Next, the {\sc uncertainty} verification stage provides the first counterexample at higher
precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
$$

@@

\blue{
For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$). Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region. Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
}

\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example. Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase. The resulting controller is:
}
$$
{
\blue{
C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
}}
$$

\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
$$
{
\blue{
C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
}}
$$

\blue{
This candidate solution is validated as the final solution by the next 
{\sc verify} phase.
}

% Counterexample from first cruisecontrol02.c benchmark with uncertainty and
% nondeterminism:
% 1) { (0.02634525299072265625, 0.9979267120361328125, -0.99768829345703125) }

% 2) { (0.02644824981689453125, 1.00053310394287109375, -1.0014629364013671875) }

% <a>
% <item>7.515781402587890625</item>
% <item>-4.385616302490234375</item>
% <item>4.142093658447265625</item>
% </a>
% <a_size>3</a_size>
% <b>
% <item>-3.52398681640625</item>
% <item>-1.530254364013671875</item>
% <item>7.58094024658203125</item>
% </b>
% <b_size>3</b_size>

>>>>

$$
\tilde G(z) = \frac{0.026506}{1.000610z+1.002838}
$$

@@

This time the {\sc uncertainty} check doesn't find any more counterexamples 
and we pass the current candidate solution to the {\sc precision} verification stage.
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
We obtain the result $false$, meaning that the current precision is insuficient.
Consequently, we increase our precision to $I_b=20,F_b=28$.
%
Since the previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. Back in the {\sc synthesise}
phase, we re-start the process with a candidate solution with all coefficients 0.
Next, the {\sc uncertainty} verification stage provides the first counterexample at higher
precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}
$$

@@

% \blue{
% For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$). Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region. Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
% }

% \blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example. Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase. The resulting controller is:
% }
% $$
% {
% \blue{
% C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
% }}
% $$

% \blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
% $$
% {
% \blue{
% C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
% }}
% $$

% \blue{
% This candidate solution is validated as the final solution by the next 
% {\sc verify} phase.
% }
